\chapter{Introduction} \label{ch:introduction}

This document will cover the concepts covered in the course Decision Support Systems and is segmented by lecture topic. This report is intended to give an overview of the methods discussed during lectures, but not to be a definitive guide to machine learning methods.

Decision support systems are a field of study that focuses on using statistical models to provide understanding of the context that is free of cognitive biases and sufficiently numerical in nature to allow computer agents to use them as the basis for making decisions despite uncertainty. As problems become more complex, the capacity of humans to gain oversight and understanding of the situation drops, and computers start needing more complex heuristics to make decisions. In both cases relying on humans adds weakness to the solution as humans tend to use few simple heuristics to make decisions, which often leads to severe and oft repeated errors\ref{http://psiexp.ss.uci.edu/research/teaching/Tversky_Kahneman_1974.pdf}.

When it comes to AI and machine learning, decision support systems can be applied to allow the machine to handle uncertainty in a systematic manner. The machine will then be able to create highly complex decision models based on available data, in ways that no human programmer could manage.

Many of the topics covered in the course rely heavily on the application of statistical methods for producing their results. As such many of the fallacies an author might make with statistics also applies to machine learning methods, 

Key points:

Correlation is not causation
    - discussed in second paragraph about biases

Why statistics?
    Why machine learning? connection to machine learning?
    - Could use more, extend third paragraph

Refer to learning goals for the course
    - Explain and discuss the general nature and applicability of decision support systems

    - Explain and discuss selected theories and methods for supervised and unsupervised learning and statistical learning with sparsity constraints

    - Apply and evaluate selected regression, classification, and clustering methods for decision support systems

    - Design, build, and evaluate decision support system prototypes
    - Explain and interpret state-of-the-art developments within decision support systems

